### 2020-09-04 S1_appendix.tex
polishing
Final touches

In this article we introduced a linear piecewise approximation of the i-CDF (inverse cumulative distribution function) to improve the computational performance of the \textit{quant} parameterisation. 
Let $\hat{F}^{-1}(\mathcal{R}_i)$ be the piecewise approximation of the i-CDF $F^{-1}(\mathcal{R}_i)$. 
The approximation consists of $n$ pieces (where $n=100$ is fixed).
Due to the nonlinear nature of small and large quantiles in a Log-normal distribution, the first and last pieces are not linear approximations but rather equal to the underlying distribution itself.

>>>>

In this article we introduced a linear piecewise approximation of the i-CDF (inverse cumulative distribution function) to improve the computational performance of the \textit{quant} parameterisation. 
Let $\hat{F}^{-1}(\mathcal{R}_i)$ be the piecewise approximation of the i-CDF $F^{-1}(\mathcal{R}_i)$. 
The approximation consists of $n$ pieces (where $n=100$ is fixed).
Due to the nonlinear nature of small and large quantiles in a log-normal distribution, the first and last pieces are not linear approximations but rather equal to the underlying distribution itself.
